---
title: "20BRS1176_EDA_Lab4"
output: html_notebook
---
ANOVA:
1. Perform Average of 3 on the following Dataset:
Year:       1    2    3    4    5    6    7    8    9    10     11     12
Sales:      5.2 4.9  5.5  4.9  5.2  5.7  5.4  5.8  5.9   6      5.2    4.8
```{r}
library(zoo)
year<-c(1:8)
Sales<-c(5.2,4.9,5.5,4.9,5.2,5.7,5.4,5.8)
Data<-data.frame(year,Sales)
rollmean(Sales,3)
```
Manual Calculation:



2. Perform Average of 3 on the following dataset:
Year:       2003    2004     2005     2006     2007     2008     2009     2010     2011     2012
Sales:       4        6        5        8        9        5        4        3        7        8
```{r}
library(zoo)
Year<-c(2003:2010)
SalesMillion<-c(4,6,5,8,9,5,4,3)
data<-data.frame(Year,SalesMillion)
rollmean(SalesMillion,3)
```
Manual Calculations:


3. Implement autocorrelation using R studio:
Autocorrelation, also known as serial correlation, is a statistical property of a time series data where the current value of a variable is related to its past values. It is a measure of the similarity between a time series and a lagged version of itself over successive time intervals.

In other words, if a time series is autocorrelated, it means that the value of the series at a given point in time is related to the value of the series at a previous point in time. This can be positive or negative, indicating whether the two values tend to move in the same direction (positive autocorrelation) or in opposite directions (negative autocorrelation).
```{r}
library(tseries)
vector1=c(34,56,23,45,21,64,78,90)
print(acf(vector1,pl=FALSE))
print(acf(vector1,lag=0,pl=FALSE))
print(acf(vector1,lag=2,pl=FALSE))
print(acf(vector1,lag=6,pl=FALSE))
```

