---
title: "20BRS1176_George Mathew EDA LAB2 L55+L56 slot"
output: html_notebook
---
Question 1. Perform multi linear regression on mtcars dataset.
```{r}
data("mtcars")
dat=mtcars[,c("mpg","disp","hp","wt")]
head(dat)
```
```{r}
library(scatterplot3d)
attach(mtcars)
scatterplot3d(wt,disp,mpg,main="3D Scatterplot")
```

```{r}
mod=lm(mpg~wt+disp)
mod
scr = scatterplot3d(wt,disp,mpg,main="3D 
scatterplot")
scr$plane3d(mod)
```

Question 2: In a random sample of 6 students each from the CSE major branch 
of 2014 and 2020, each student was asked about their salary package 
after they completed graduation. We wanted to know if the typical 
salary offered after graduation had changed over the past 6 years.
```{r}
b2014=c(667,859,1129,500,1098,1036) 
b2020=c(920,1060,800,645,869,1101)
x1b=mean(b2014)
x2b=mean(b2020)
s1=sd(b2014)
s2=sd(b2020)
n1=length(b2014)
n2=length(b2020)
```

```{r}
diff_in_means=x1b-x2b
SE_diff_mean=sqrt((s1^2/n1)+(s2^2/n2))
t_stat=diff_in_means/SE_diff_mean
t_stat
pval=2*pt(t_stat,df=n1+n2-2)
pval
```
Interpretation:
Hence, we got the p value as 0.89 which is greater than the default assumption. 
By this we can say that there is not much difference between the mean pay 
offered to students in 2014 and 2020.


Question 3: Testing of hypothesis(z proportion)
A. Out of a sample of 1000 people, 300 watched movies in theatres 
before the pandemic. In a sample of 1200 persons, it was discovered 
that 350 of them watched movies in theatres after the outbreak. We 
wish to investigate whether there is a decline in theatre attendance 
following the pandemic at the 5% level of significance.
```{r}
prop.test(x=c(300,350), n=c(1000,1200),,alternative = "two.sided")
```
Interpretation:
x-squared values is 0.144 and p-values is 0.7042. the alternate hypothesis is that 
there is no decline in theatre attendance. Since the obtained p-value is 0.7042 is 
less than the assumed level of significance 0.05, we can reject the hypothesis.

B.Perform two-proportion Z-Test
```{r}
prop.test(x=c(800,900),n=c(1000,1200),alternative ="greater")
```

Question 4:Estimate the correlation coefficient using pearson correlation and 
spearman rank correlation. Solve using manual method and R code.

```{r}
x <- c(45,50,53,58,60)
y <- c(9,8,8,7,5)
#Pearson Method
cor(x,y,method = "pearson")
#Spearman Method
cor(x,y,method = "spearman")
```
Manual Calculations:
