---
title: "20BRS1176_George Mathew EDA LAB3 L55+L56 slot"
output:
  pdf_document: default
  html_notebook: default
---
1.Our company is testing a new drug that reduces hypertension. A 
total of 14000. individuals with high blood pressure (r= 150 mmlg, 
SD= 10 mmlg) are given the drug for a month, and then their blood 
pressure is measured again. The mean systolic blood pressure has 
decreased to 144 mmitz, with a standard deviation of 9 mmHg
```{r}
before <- rnorm(14000, 150, 10)
after <- rnorm(14000, 144, 9) 
t.test(before, after,paired = TRUE)
```
Interpretation:
Since the p-value is below the significance level, we may state with certainty that the new drug does lower blood pressure.

2. The following table gives monthly sales (in thousand rupees) of a 
certain firm in the 3 states by its four salesmen:
States:           Salesman
          I       II        III       IV
A         6       5          3        8
B         8       9          6        5   
C         10      7          8        2
Setup the analysis of variance table and test whether there is any 
significant difference (i) between the salesmen (ii) between sales in the 
states.
```{r}
A <- c(6,5,3,8)
B <- c(8,9,6,5)
C <- c(10,7,8,7)
summary (aov (A~B + C))
```

```{r}
States <- c('A', 'B', 'C')
I <- c (6,8,10)
II <- c (5,9,7)
III <- c (3,6,8)
IV <- c (8,5,7)
df <- data.frame (States, I, II, III, IV)
a <- aov (I ~ II + III + III)
summary(a)
```
Interpretation:
There is no reasonable difference between the states